|

### 2025-07-09 output/IMPS-2025-slideshow.qmd
Add "null probability" argument slide

The second, that constrain that you see there, implies that the item is represented in an orthogonal basis.
That is the reason why the discrimination is defined by a "general Pythagorean theorem".
:::

## Assumptions: Increasing monotony {.smaller}

<!-- TODO: Put in column and make figure in 2nd column taller -->

---@reckase_difficulty_1985 [p. 402]

::::: {.columns .fragment}
::: column
<br>

@@

>>>>

The second, that constrain that you see there, implies that the item is represented in an orthogonal basis, which is why the discrimination is defined by a "general Pythagorean theorem".

So, our purpose in this work is **to relax these two assumptions**.
:::

## Assumptions: Increasing monotony

::::: columns
::: column
<br>

@@

::: column
```{r m2pl-representation-unidimensional}
#| fig-align:  center
#| fig-height: 7.2
#| fig-width:  7.2

::: notes
In the first case, one may argue that we may deal with "undimensional items" or, more generally, items that have null discrimination components.

This would imply that the probability of a correct response would not change with respect to that dimension; i.e., that trait is not being measured by the item, so the isoprobability lines would be parallel to the $\theta_2$ axis (in this example.

Therefore, the probability does not "increase monotonically".

Nevertheless, with this caveat about null discrimination components, this assumption would be realistic in a "cognitive testing context": The more you know, the more likely you are to give a correct answer.
:::
